A fully labelled proof system for intuitionistic modal logics

### 2021-01-14 FullyLabelled/JLC/conclusion.tex
margins fixed

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
\todo{The frame properties and rules considered in the paper under review are all of the geometric form,
	so it would be more correct to say that it is an in-depth study of intuitionistic modal logic for a larger
	class of geometric frame properties rather than a generalization of the results in the paper by
	Maffezioli,  Naibo and Negri .}\sonia{OK}
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.

@@

\todo{In references, book and theses titles should be capitalized (this is not done consistently).} \marianela{book title or the chapter as well?} \sonia{OK}

\todo{DG019 change to published reference}\sonia{OK}

>>>>

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.

@@
